Blame and Coercion: Together Again for the Second Time

### 2019-10-16 paper.tex
let ... ranges => let ... range

Let $ e $ ranges over terms, including all terms from $ \mathtt{STLC+} $ and, 
in addition, casts and blame. Unlike $ \mathtt{STLC+} $, we annotate the 
codomain of lambda abstractions explicitly.
\todo[inline]{Why do you annotate the codomain of lambda abstractions
  explicitly? -Jeremy}
\todo[inline]{Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
The end of \figref{fig:blame-static} shows the typing rules for the
additional terms.

Let $ o $ ranges over observations. They are what would be observed if a 
program terminates. Observations include all value constructors and blame.

@@

Let $ c $ range over casts. A cast is a triple of a type, a label, and a type.
Let $ v $ range over values. A value is either a function, the 
element of unit, a pair, a left injection, a right injection, or a casted value.
The cast around a casted value is not arbitrary, as shown by value typing: the 
source type must be a pre-type, and the source and the target must be 
shallow-consistent.
Let $ r $ ranges over cast results. A cast result is either a success, which 
brings a value, or a failure, which brings a blame label.
Let $ s $ ranges over machine states. A state is either looking at an 
expression to decide what to do next, returning a value to a continuation, or 
halting with an observation.
Let $ \kappa $ ranges over continuations. $ \mathtt{mt} $ is the top 
continuation. The remaining continuations correspond to expressions. For 
example, $ (\mathtt{cons_1} \; e \; \rho \; \kappa) $ is the continuation where 
we are waiting for the value of the first argument to a $ \mathtt{cons} $. And 
the last continuation, $ \langle c \rangle \kappa $ is to cast the value before 
returning to $ \kappa $.

@@

\figref{fig:normal-coercion} defines the normal coercion.
\todo[inline]{Give a summary statement about the shape of the normal form.}
Types, pre-types, and blame labels are as before.
Let $ I $ ranges over injectable types. An injectable type is a type that can 
be cast directly to (injection) and from (projection) $ \TOOdyn $. The 
definition of injectable type depends on blame strategy. With \lazyD, all 
pre-types are injectable. With \lazyUD, only $ \POOfun{\TOOdyn}{\TOOdyn} $ 
is injectable. 
Let $ c $ ranges over coercions, a coercion is either injection, projection, 
identity, failure, sequencing, or function coercion.
Let $ \bar{c} $ ranges over wrapper coercions, which represent casts in $ 
\vOOcast{v}{c} $.
Let $ \hat{c} $ ranges over normal coercions. If we inline $ \bar{c} $ and 
re-arrange cases a little bit, the definition becomes:
\todo[inline]{Be more specific than ``a little bit''. -Jeremy}
\[
\begin{array}{rclr}
\stxrule{\hat{c}}{normal coercions}{
	\ncFun{\hat{c}}{\hat{c}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFail{l}}
}
\stxrulecont{
	\ncId \mid
	\ncProj{I}{l} \mid
	\ncInj{I} \mid
	\ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
	\ncFail{l} \mid
}
\end{array}
\]

@@

Let $ c $ ranges over hypercoercions. A hypercoercion is either 
an identity cast between the dynamic types, or a complex including a head, a 
middle, and a tail. 
Let $ h $ ranges over heads. A head is either a no-op, or a projection.
Let $ m $ ranges over middles. There is a one-to-one 
correspondence between middles and type constructors. 
We generalize shallow-consistency to middles $ m \smile m $ in the natural way.
Let $ t $ ranges over tails. A tail is either a no-op, an injection, or a 
failure. 
Let $ \ell $ ranges over no-op and labels. It is useful when we introduce 
composition of hypercoercions.

@@

\figref{machine-cekcc} defines the machine. 
Let $ v $ ranges over value. A value is either the unit value, function, pair, 
left injection of sum, right injection of sum, and injection to $ \TOOdyn $.
Cast results ($ r $) and machine states ($ s $) are as before. 
Let $ \kappa $ ranges over continuations and let $ k $ ranges over 
pre-continuations. 
A continuation is now a pair where the first part is a cast and the second 
part is a pre-continuation. 
Pre-continuation are like the continuations before.

>>>>

Let $ e $ range over terms, including all terms from $ \mathtt{STLC+} $ and, 
in addition, casts and blame. Unlike $ \mathtt{STLC+} $, we annotate the 
codomain of lambda abstractions explicitly.
\todo[inline]{Why do you annotate the codomain of lambda abstractions
  explicitly? -Jeremy}
\todo[inline]{Because I apply $ id(\cdot) $ to the codomain in the HC CEK. -KC}
The end of \figref{fig:blame-static} shows the typing rules for the
additional terms.

Let $ o $ range over observations. They are what would be observed if a 
program terminates. Observations include all value constructors and blame.

@@

Let $ c $ range over casts. A cast is a triple of a type, a label, and a type.
Let $ v $ range over values. A value is either a function, the 
element of unit, a pair, a left injection, a right injection, or a casted value.
The cast around a casted value is not arbitrary, as shown by value typing: the 
source type must be a pre-type, and the source and the target must be 
shallow-consistent.
Let $ r $ range over cast results. A cast result is either a success, which 
brings a value, or a failure, which brings a blame label.
Let $ s $ range over machine states. A state is either looking at an 
expression to decide what to do next, returning a value to a continuation, or 
halting with an observation.
Let $ \kappa $ range over continuations. $ \mathtt{mt} $ is the top 
continuation. The remaining continuations correspond to expressions. For 
example, $ (\mathtt{cons_1} \; e \; \rho \; \kappa) $ is the continuation where 
we are waiting for the value of the first argument to a $ \mathtt{cons} $. And 
the last continuation, $ \langle c \rangle \kappa $ is to cast the value before 
returning to $ \kappa $.

@@

\figref{fig:normal-coercion} defines the normal coercion.
\todo[inline]{Give a summary statement about the shape of the normal form.}
Types, pre-types, and blame labels are as before.
Let $ I $ range over injectable types. An injectable type is a type that can 
be cast directly to (injection) and from (projection) $ \TOOdyn $. The 
definition of injectable type depends on blame strategy. With \lazyD, all 
pre-types are injectable. With \lazyUD, only $ \POOfun{\TOOdyn}{\TOOdyn} $ 
is injectable. 
Let $ c $ range over coercions, a coercion is either injection, projection, 
identity, failure, sequencing, or function coercion.
Let $ \bar{c} $ range over wrapper coercions, which represent casts in $ 
\vOOcast{v}{c} $.
Let $ \hat{c} $ range over normal coercions. If we inline $ \bar{c} $ and 
re-arrange cases a little bit, the definition becomes:
\todo[inline]{Be more specific than ``a little bit''. -Jeremy}
\[
\begin{array}{rclr}
\stxrule{\hat{c}}{normal coercions}{
	\ncFun{\hat{c}}{\hat{c}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFail{l}}
}
\stxrulecont{
	\ncId \mid
	\ncProj{I}{l} \mid
	\ncInj{I} \mid
	\ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
	\ncFail{l} \mid
}
\end{array}
\]

@@

Let $ c $ range over hypercoercions. A hypercoercion is either 
an identity cast between the dynamic types, or a complex including a head, a 
middle, and a tail. 
Let $ h $ range over heads. A head is either a no-op, or a projection.
Let $ m $ range over middles. There is a one-to-one 
correspondence between middles and type constructors. 
We generalize shallow-consistency to middles $ m \smile m $ in the natural way.
Let $ t $ range over tails. A tail is either a no-op, an injection, or a 
failure. 
Let $ \ell $ range over no-op and labels. It is useful when we introduce 
composition of hypercoercions.

@@

\figref{machine-cekcc} defines the machine. 
Let $ v $ range over value. A value is either the unit value, function, pair, 
left injection of sum, right injection of sum, and injection to $ \TOOdyn $.
Cast results ($ r $) and machine states ($ s $) are as before. 
Let $ \kappa $ range over continuations and let $ k $ range over 
pre-continuations. 
A continuation is now a pair where the first part is a cast and the second 
part is a pre-continuation. 
Pre-continuation are like the continuations before.
